Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-04-29 SupportingInformation.Rmd
minor edits in evo-cop histogram plot as instructed by DCR

<!--adding plots showing results to confirm hypothesis behind third mechanism-->
\begin{figure}[!h]
\textbf{ \hspace{6.5 cm} (A) \hspace{2 cm} (B) \hspace{2 cm} (C)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/ExtremeL_hist_taildep.pdf}\\
\end{center}
\textbf{ \hspace{6.5 cm} (D) \hspace{2 cm} (E) \hspace{2 cm} (F)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/SomewhatL_hist_taildep.pdf}\\
\end{center}
\textbf{ \hspace{6.5 cm} (G) \hspace{2 cm} (H) \hspace{2 cm} (I)} \\
\vspace{-0.7 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/BivNormal_hist_taildep.pdf}\\
\end{center}
\textbf{ \hspace{6.5 cm} (J) \hspace{2 cm} (K) \hspace{2 cm} (L)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/SomewhatR_hist_taildep.pdf}\\
\end{center}
\textbf{ \hspace{6.5 cm} (M) \hspace{2 cm} (N) \hspace{2 cm} (O)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/ExtremeR_hist_taildep.pdf}\\
\caption[Non-parametric statistics to check probable mechanism behind asymmetric tail dependence in character distributions across phylogeny tips]{Three measures of asymmetric tail dependence using non-parametric statistics ($\cor,\Ps$ and $\Dsq$)
on lower ($l_b=0,u_b=0.2$) and upper ($l_b=0.8,u_b=1$) tips confirms our hypothesis that copula structure in evolutionary changes in bivariate characters can give rise to similar tail dependent copula in character distributions across phylogeny tips (for details see Appendix \ref{evol_mech}). Stronger lower tail dependence (distributed more on positive values) was found in bivariate traits when (A-C) extreme left tail and (D-F) moderately left tail dependent copula was used in evolutionary shifts through each branch. Similarly, non-parametric statistics showed symmetric tail dependence for (G-I) normal copula and stronger upper tail dependence for (J-L) moderately right tail and (M-O) extreme right tail dependent copula, respectively.\label{fig_cop_evo}}
\end{center}
\end{figure}

>>>>

<!--adding plots showing results to confirm hypothesis behind third mechanism-->
\begin{figure}[!h]
\textbf{ \hspace{6.5 cm} (A) \hspace{2 cm} (B) \hspace{2 cm} (C)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/ExtremeL_hist_taildep.pdf}\\
\end{center}
\textbf{ \hspace{6.5 cm} (D) \hspace{2 cm} (E) \hspace{2 cm} (F)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/SomewhatL_hist_taildep.pdf}\\
\end{center}
\textbf{ \hspace{6.5 cm} (G) \hspace{2 cm} (H) \hspace{2 cm} (I)} \\
\vspace{-0.7 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/BivNormal_hist_taildep.pdf}\\
\end{center}
\textbf{ \hspace{6.5 cm} (J) \hspace{2 cm} (K) \hspace{2 cm} (L)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/SomewhatR_hist_taildep.pdf}\\
\end{center}
\textbf{ \hspace{6.5 cm} (M) \hspace{2 cm} (N) \hspace{2 cm} (O)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/ExtremeR_hist_taildep.pdf}\\
\caption[Non-parametric statistics to check probable mechanism behind asymmetric tail dependence in character distributions across phylogeny tips]{Three measures of asymmetric tail dependence using non-parametric statistics ($\cor,\Ps$ and $\Dsq$)
on lower ($l_b=0,u_b=0.2$) and upper ($l_b=0.8,u_b=1$) tips confirms our hypothesis that copula structure in evolutionary changes in bivariate characters can give rise to similar tail dependent copula in character distributions across phylogeny tips (for details see Appendix \ref{evol_mech}). Stronger lower tail dependence (distributed more on positive values) was found in bivariate traits when (A-C) extreme left tail and (D-F) moderately left tail dependent copula was used in evolutionary shifts through each branch. Similarly, non-parametric statistics showed symmetric tail dependence for (G-I) normal copula and stronger upper tail dependence for (J-L) moderately right tail and (M-O) extreme right tail dependent copula, respectively. The number $(n)$ in each subfigure designates how many statistics out of $100$ is equal or less than $0$, thus if $n$ is substantially lower (or higher) than $50$, it would indicate asymmetric left (or right) tail-dependence in evolved traits-copula. \label{fig_cop_evo}}
\end{center}
\end{figure}
